---
output:
  pdf_document: default
  html_document: default
---

```{r}
library(tidyverse)
library(rms)
library(readr)
pbc=read.table("~/Desktop/Microbiome signature-HSZ.txt",head=TRUE)
head(pbc)
dd<-datadist(pbc)
pbc$L5likevirus <- cut(pbc$L5likevirus,breaks=c(-Inf, 2, 4, Inf),
                   labels=c("low","medium","high"))
pbc$event <- pbc$Event==1

head(pbc)
```


```{r}
options(datadist="dd")
options(na.action="na.delete")
summary(pbc$time)
coxpbc<-cph(formula = Surv(time,died) ~  age + catbili + sex + copper + stage + trt ,data=pbc,x=T,y=T,surv = T,na.action=na.delete)  #,time.inc =2920

print(coxpbc)
surv<-Survival(coxpbc) 
surv3<-function(x) surv(1825,x)
surv4<-function(x) surv(2920,x)

x<-nomogram(coxpbc,fun = list(surv3,surv4),lp=T,
            funlabel = c('5-year survival Probability','8-year survival Probability'),
            maxscale = 100,fun.at = c(0.95,0.9,0.8,0.7,0.6,0.5,0.4,0.3,0.2,0.1))

pdf("nomogram_classical.pdf",width = 12,height = 10)
plot(x, lplabel="Linear Predictor",
     xfrac=.35,varname.label=TRUE, varname.label.sep="=", ia.space=.2, 
     tck=NA, tcl=-0.20, lmgp=0.3,
     points.label='Points', total.points.label='Total Points',
     total.sep.page=FALSE, 
     cap.labels=FALSE,cex.var = 1.6,cex.axis = 1.05,lwd=5,
     label.every = 1,col.grid = gray(c(0.8, 0.95)))
dev.off()